Fluid-mechanical erosion creates anisotropic porous media

### 2022-05-19 docs/PhysicsPaper/StokesErosion.tex
NM

\author{Nicholas J.~Moore}
%\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\author{Bryan D.~Quaife}
%\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\author{Shang-Huan Chiu}
%\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}

@@

@@

Therefore we have the relationship
\begin{equation}
\label{ResistDrag}
1/k \approx \frac{1}{4 U}  \, \FD \cdot \ex
\end{equation}

@@

The total anisotropy is the produce of the shape and configurational
\begin{equation}
\anis = \anis_S \anis_C
\end{equation}

@@

>>>>

\author{Nicholas J.~Moore}
%\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}

\author{Jake Cherry}
%\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}

\author{Shang-Huan Chiu}
%\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, FL, 32306.}

\author{Bryan D.~Quaife}
%\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}

@@

\nick{Perhaps you can combine the real BIE and Cauchy representation into one section to condense it and to make the complex analysis take more center stage.}

@@

Therefore we have the relationship
\begin{equation}
\label{ResistDrag}
1/k_1 \approx \frac{1}{4 U}  \, \FD \cdot \ex
\end{equation}

@@

The total anisotropy is the product of the shape and configurational
\begin{equation}
\anis = \anis_S \anis_C
\end{equation}

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig4}
\includegraphics[width = 0.99 \textwidth]{./figs/fig4.pdf}
\caption{
a) Statistics from an ensemble of runs.
}
\end{figure*}
%---------------------------------------------------------%
% Data from 100-3
